Verifying Demonstrations

### 2018-08-23 paper/adversary-model.tex

\begin{definition}[Base witness adversary]\label{base-witness-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W)\) and the time it took place, 
  \(t_{P,W}\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(S\).
\end{definition}

@@

\begin{figure}
  \centering
  \includegraphics{base-witness-adversary.tikz}
  \caption{\label{fig:witness-adversary}%
    An overview of the base witness adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W)\), and the 
    time it happened, \(t_{P,W}\).
    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{W,S}\).
    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

>>>>

\begin{definition}[Base witness adversary]\label{base-witness-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W, l)\) and the time it took place, 
  \(t_{P,W}\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(S\).
\end{definition}

@@

\begin{figure}
  \centering
  \includegraphics{base-witness-adversary.tikz}
  \caption{\label{fig:witness-adversary}%
    An overview of the base witness adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W, l)\), and 
    the time it happened, \(t_{P,W}\).
    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{W,S}\).
    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

### 2018-08-23 paper/intro.tex

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{system-model}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{related-work}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{building-blocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
Finally, we conclude with a discussion \cref{Discussion} and future work in \cref{Conclusion}.

>>>>

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.

### 2018-08-23 paper/privacy-properties.tex
Adds comment on core privacy property

@@

\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.

@@

Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt, because being counted implies support for a cause. This also means that besides physical force, coercion can happen by forcing the participate to show a receipt. We thus have to decide between individual verifiability and the privacy properties for e-voting or define privacy properties suitable for the scenario. The ultimate privacy requirement is thus stronger here: in contrast to voting, where it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.

The privacy properties we need in this context are the following:
\begin{description}
  \item[Involuntary participant unlinkability:] unless the participant 
    discloses the receipt (by revealing her identity), there is no link between 
    the protest data on the ledger and the identity of the participant.

  \item[Involuntary witness unlinkability:] unless the witness discloses the 
    receipt (by revealing her identity), there is no link between the protest 
    data on the ledger and the identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

>>>>

\daniel{The main idea is that the adversary cannot link the protester's real 
  identity \(P\) to the protest cause \cid.}

@@

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against 
her will.
Receipt freeness, while desirable, is not \emph{always} desirable.
For instance, the location proof might be useful to prove presence to a third 
party, \eg for strengthening the authenticity of witness information.

Thus privacy remains.
For the protester we want unlinkability between a protester's real identity 
\(P\) and the cause identifier \(\cid\).
For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\).

\daniel{End of edits so far.}

@@

Given that all conditions for being counted in a protest are met, individual 
verifiability implies a receipt \daniel{no, I know my proof is included in 
  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
  hence receipt-freeness} because being counted implies support for a cause. 
This also means that besides physical force, coercion can happen by forcing the 
participate to show a receipt. \daniel{The only receipt we have is the private 
  key of the protester, with that key the adversary can compute \(\pid = 
    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
We thus have to decide between individual verifiability and the privacy 
properties for e-voting or define privacy properties suitable for the scenario. 
The ultimate privacy requirement is thus stronger here: in contrast to voting, 
where it is the content of the vote itself that needs to be unlinkable to the 
voter, here the fact of having cast a vote at all needs to be unlinkable.

The privacy properties we need in this context are the following:
\begin{description}
  \item[Involuntary participant unlinkability:] \daniel{the name has a 
      double-negative ring to me} unless the participant discloses the receipt 
    (by revealing her identity), there is no link between the protest data on 
    the ledger and the identity of the participant.

  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
      too of course} unless the witness discloses the receipt (by revealing her 
    identity), there is no link between the protest data on the ledger and the 
    identity of the witness.
\end{description}
\sonja{old}
In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

### 2018-08-23 paper/verifiability-properties.tex

We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
Indeed, all three situations correspond to cases in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more formally in the context of protest, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
    \end{requirements}

>>>>

We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
Indeed, all three situations correspond to cases in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
(We discuss privacy in \cref{privacy-properties}.)

We draw inspiration from the three general desirable properties for 
verifiability, as summarized by 
\textcite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that 
anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more in the context of protests, we define three 
verifiability requirements, among which eligibility can be further broken up 
into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
    \end{requirements}
